Article Title

### 2019-11-08 text/02-methods.Rmd
Remove annotations with modifiers during cleanup
Update ADS paper reference

1. Any annotations where the GO accession was marked as obsolete were removed.
2. Some terms in the GO have 'alternative ids'. When naively removing duplicates, two entries will not be recognized as duplicates if they have different accessions pointing to the same GO term. Therefore, all GO accessions were changed to their respecitve 'main id' and the dataset was again scanned for duplicates.

@@

## Quality Evaluation
Quality evaluation of gene function predictions is not trivial and usually done by comparing the set of predicted functions of a gene against a *gold standard* consisting of annotations that are assumed to be correct.
We used annotations that were created or in some way curated with human participation for gold standards.
There are a plethora of different metrics to perform the comparison of predictions against this gold standard.
When we first published GOMAP [@Wimalanathan2018], we used a modified version of the hierarchical evaluation metrics originally introduced in [@Verspoor2006] because they were simple, clear, and part of an earlier attempt at unifying and standardizing GO annotation comparisons [@Defoin-Platel2011].
In the meantime, @Plyusnin2018 have published an approach for evaluating different metrics showing substantial differences within the robustness of different approaches.
`TODO DESCRIBE THEIR APPROACH`
We have applied their method on the Gold Standards available to us to determine which evaluation metric is the most appropriate in our case.
The results of this analysis can be seen in `TODO`.

>>>>

1. Any annotations where the GO accession was marked as obsolete were removed.
2. Some terms in the GO have 'alternative ids'. When naively removing duplicates, two entries will not be recognized as duplicates if they have different accessions pointing to the same GO term. Therefore, all GO accessions were changed to their respecitve 'main id' and the dataset was again scanned for duplicates.
3. Any annotations with modifiers (NOT, contributes_to...) were removed since no tool used in the further analysis can handle them.

@@

## Quality Evaluation
Quality evaluation of gene function predictions is not trivial and usually done by comparing the set of predicted functions of a gene against a *gold standard* consisting of annotations that are assumed to be correct.
We used annotations that were created or in some way curated with human participation for gold standards.
There are a plethora of different metrics to perform the comparison of predictions against this gold standard.
When we first published GOMAP [@Wimalanathan2018], we used a modified version of the hierarchical evaluation metrics originally introduced in [@Verspoor2006] because they were simple, clear, and part of an earlier attempt at unifying and standardizing GO annotation comparisons [@Defoin-Platel2011].
In the meantime, @Plyusnin2019 have published an approach for evaluating different metrics showing substantial differences within the robustness of different approaches.
`TODO DESCRIBE THEIR APPROACH`
We have applied their method on the Gold Standards available to us to determine which evaluation metric is the most appropriate in our case.
The results of this analysis can be seen in `TODO`.
